% !TEX program = xelatex
% Tejas Pawar — One-page resume

\documentclass[10pt,letterpaper]{article}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}

\geometry{margin=0.6in, top=0.5in, bottom=0.5in}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\titlespacing*{\section}{0pt}{8pt}{4pt}
\titleformat{\section}{\normalfont\bfseries\uppercase}{}{0em}{}[\vspace{-2pt}\titlerule\vspace{4pt}]

\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=black}
\pagestyle{empty}

\begin{document}

% --- Header ---
\begin{center}
  {\fontsize{18}{20}\selectfont\textbf{Tejas Pawar}}\\[4pt]
  \href{mailto:tejasp@udel.edu}{tejasp@udel.edu} \textbar{} +1 (302) 444-2983 \textbar{} \href{https://github.com/tejaspawar12}{GitHub} \textbar{} \href{https://www.linkedin.com/in/pawar-tejas123/}{LinkedIn}
\end{center}
\vspace{2pt}

% --- Summary ---
\section*{Summary}
AI Systems Engineer with experience in machine learning and GenAI infrastructure. Design deterministic + LLM hybrid systems, retrieval-augmented pipelines, and scalable backend APIs with Python and FastAPI. Skilled in model training, evaluation, and data pipelines; deploy and maintain systems on AWS and Docker. Build reliable, grounded AI systems with measurable outcomes.

% --- Experience ---
\section*{Experience}

\textbf{Graduate Assistant (IT-ATS)} \hfill June 2025 -- May 2026\\
University of Delaware, Academic Technology Services \textbar{} Newark, Delaware, USA
\begin{itemize}[leftmargin=*, nosep, topsep=1pt]
  \item Contributed to AWS-based AI infrastructure for StudyAiDE and PATHS Engine platforms.
  \item Designed and implemented retrieval-augmented AI pipelines integrating Neo4j knowledge graphs with vector-based search systems.
  \item Developed contextual faculty AI agents using AWS Bedrock for model inference and structured tool-based workflows.
  \item Built backend API services (FastAPI) to support AI-driven academic tools.
  \item Used AWS services (Bedrock, RDS, S3, IAM) for deployment and cloud workflows.
  \item Contributed to model fine-tuning and training workflows to adapt foundation models for domain-specific academic use cases.
  \item Implemented Docker-based multi-service architecture separating API, database, and AI inference layers.
\end{itemize}

\vspace{2pt}
\textbf{Machine Learning Engineer Intern} \hfill March 2023 -- July 2023\\
LogicMo Systems Private Limited \textbar{} Pune, India
\begin{itemize}[leftmargin=*, nosep, topsep=1pt]
  \item Developed computer vision models for vehicle object detection using YOLO architecture implemented in TensorFlow.
  \item Built an end-to-end data pipeline converting raw video streams into structured image datasets for supervised training.
  \item Designed preprocessing workflows including frame extraction, resizing, normalization, and augmentation to improve model generalization.
  \item Trained and optimized detection models through systematic hyperparameter tuning (learning rate, batch size, anchor configurations, optimizer selection).
  \item Achieved 0.97 mAP on validation dataset, improving object detection reliability for vehicle-based use cases.
\end{itemize}

% --- Education ---
\section*{Education}

\textbf{M.S. in Data Science} \hfill May 2026\\
University of Delaware, USA\\
Relevant: Applied ML, NLP, Data Mining, Algorithm Design, Unstructured Data Analytics, Ethical AI, DBMS.

\textbf{B.E. in Electronics \& Telecommunication Engineering (Honors in Data Science)} \hfill May 2024\\
Savitribai Phule Pune University, India\\
Relevant: Machine Learning, Deep Learning, Data Structures \& Algorithms, Probability \& Statistics.

% --- Technical Skills ---
\section*{Technical Skills}
Python, SQL, Generative AI, Agentic AI, Retrieval-Augmented Generation (RAG), Reinforcement Learning, Hyperparameter Tuning, Natural Language Processing (NLP), Computer Vision, LLM Integration, OpenAI API, PostgreSQL, MySQL, Neo4j, vector databases, TensorFlow, PyTorch, Keras, Scikit-learn, MLlib, NumPy, Pandas, SciPy, AWS, Docker, CI/CD, GitHub Actions.

% --- Project ---
\section*{Project}

\href{https://enchanting-heart-production.up.railway.app/}{\textbf{Live}} \textbar{} \textbf{AI-Powered Fitness Coach} \textbar{} \textit{Full-Stack Cross-Platform Application}\\[-8pt]
\begin{itemize}[leftmargin=*, nosep, topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=0pt]
  \item Built and deployed a full-stack fitness application with FastAPI backend and cross-platform React Native (iOS, Android, Web) frontend using a single codebase.
  \item Designed secure JWT authentication (access + refresh tokens) and integrated Claude for an AI coach with daily guidance, multi-turn chat, and automated weekly progress narratives; added usage tracking and fallback handling.
  \item Designed 15+ REST endpoints using SQLAlchemy 2 ORM, Pydantic validation, dependency-injected auth, and Alembic-managed PostgreSQL schema migrations.
  \item Implemented offline-first design (Zustand + AsyncStorage) with mutation queue and background sync so users can log workouts without connectivity; deployed backend and frontend on Railway.
\end{itemize}


\end{document}
